

```{r}
#| include: false

# Importing packaegs, functions declaring globals
source("R/packages.R")
source("R/utils.R")
source("R/globals.R")
source("R/functions.R")
source("R/dataprep_functions.R") # Preparing specialized (non-generic) functions
source("R/viz_functions.R")

# Preparing data
source("R/0_dataprep.R")

# Groups to use for disaggregation
groups <- GROUPS[c("resp_all", "hh_urbrur", "resp_gender", "resp_age_agg3_str", "resp_income_agg3_str")]

```

## Managing day-to-day

### Managing food expenses

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mfhi_m2d2_food
#| echo: false
#| warning: false
#| fig-cap: "Managing food expenses"
#| cap-location: margin

fig_notes <- ""

indicators <- c("mfhi_f_p1mo_wwo_yes", "mfhi_f_p1mo_wwo_no", "mfhi_f_p1mo_wwo_dkr", 
                "mfhi_f_p1mo_wwo_ti12", "mfhi_f_p1mo_wwo_ti310", "mfhi_f_p1mo_wwo_ti10",  "mfhi_f_p1mo_wwo_napp", 
                "mfhi_f_p12mos_wwo_yes", "mfhi_f_p12mos_wwo_no", "mfhi_f_p12mos_wwo_dkr", "mfhi_f_p12mos_wwo_napp")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = FALSE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

branch_levels <- c("Yes", "No", "Don't know/refused", "1-2 times", "3-10 times", "More than 10 times", "Not applicable")
fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.05) %>% 
  mutate(indicator_branch = fct_rev(factor(indicator_branch, levels= branch_levels, ordered = TRUE)))

labels <- list(
  title = "Food security",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#CEE5F2", "#DD99BB", "grey90", "#E8DDB5", "#92B6B1", "#788AA3")
names(palette) <- c("Yes", "No", "Don't know/refused", "Not applicable", "1-2 times", "3-10 times", "More than 10 times")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### MFHI Component indicator #1
```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-mfhi_m2d2_food_main
#| echo: false
#| warning: false
#| fig-cap: "MFHI #1: Managing food expenses"
#| cap-location: margin

fig_notes <- ""

indicators <- c("mfhi_f_secure")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 80, indicator_stem = 30, indicator_branch = 40, group_name = 80, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = "Sustained household food security over 12 months",
  subtitle =  "MFHI Component Indicator #1",
  yax_ti = "Adults (% 18+)",
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", fill = "#41BBD9", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_vjust = 1, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "red")
)

scales <- list(
  fillcolor = NULL, 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### Managing core non-food expenses
```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mfhi_m2d2_nonfood
#| echo: false
#| warning: false
#| fig-cap: "Managing core non-food expenses"
#| cap-location: margin

fig_notes <- ""

indicators <- names(int_data)[str_detect(names(int_data), "mfhi_nf")]
indicators <- indicators[!str_detect(indicators, "yapp|mfhi_nf_tot_cp|mfhi_nf_secure|mfhi_nf_secure_notmiss")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = "Ability to pay core non-food expenses",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#CEE5F2", "#FF9F1C")
names(palette) <- c("Yes", "No", "Not applicable")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_category",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### MFHI Component indicator #2

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-mfhi_m2d2_nonfood_main
#| echo: false
#| warning: false
#| fig-cap: "MFHI #2: Managing core non-food expenses"
#| cap-location: margin

fig_notes <- "Notes: This indicator is a composite, constructed using four questionnaire items asking whether the respondent has been unable to pay expenses in the past month related to: (1) Housing, (2) Energy, (3) Water and (4) Transportation. The indicator is constructed only considering the expenses that are applicable to the household."
  
indicators <- c("mfhi_nf_secure")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 80, indicator_stem = 30, indicator_branch = 40, group_name = 80, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = "Able to pay all applicable core non-food expenses in past 1 month",
  subtitle =  "MFHI Component Indicator #2",
  yax_ti = "Adults (% 18+)",
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", fill = "#41BBD9", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_vjust = 1, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "red")
)

scales <- list(
  fillcolor = NULL, 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### Managing debt

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-md2d_debt
#| echo: false
#| warning: false
#| fig-cap: "MSEs by sector of production"
#| cap-location: margin

fig_notes <- "Notes: This figure is based on responses to the following question: Think about the money you owe (for example to a bank, MFI, SACCO, a shopkeeper, friends or family or a loan you took over the phone). In the past 3 months have you had to reduce spending on food to repay any money that you owe?"

indicators <- names(int_data)[str_detect(names(int_data), "mfhi_d_p3mo_stress")]
indicators <- indicators[!str_detect(indicators, "notmiss")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = "Difficulty repaying debt",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#CEE5F2", "#FF9F1C", "#DD99BB")
names(palette) <- c("Yes", "No", "Not applicable (Does not owe money)", "Don't know/refused")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1.003), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### MFHI Component indicator #3


```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-mfhi_md2d_debt_main
#| echo: false
#| warning: false
#| fig-cap: "MFHI #3: Managing debt"
#| cap-location: margin

fig_notes <- "Notes: This indicator is based on responses to a single question: Think about the money you owe (for example to a bank, MFI, SACCO, a shopkeeper, friends or family or a loan you took over the phone). In the past 3 months have you had to reduce spending on food to repay any money that you owe?"
  
indicators <- c("mfhi_d_secure")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 80, indicator_stem = 30, indicator_branch = 40, group_name = 80, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = "Able to service debt without reducing food spending",
  subtitle =  "MFHI Component Indicator #3",
  yax_ti = "Adults (% 18+)",
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", fill = "#41BBD9", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_vjust = 1, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "red")
)

scales <- list(
  fillcolor = NULL, 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

## Coping with risk

### Access to emergency funds

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-risk_ef
#| echo: false
#| warning: false
#| fig-cap: "Access to emergency funds"
#| cap-location: margin

indicators <- names(int_data)[str_detect(names(int_data), "mfhi_ef_30d_srcany")]
indicators <- indicators[!str_detect(indicators, "notmiss|difsmeornot|difany")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.05) 

labels <- list(
  title = "Access to emergency funds",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, "Notes: This figure is based on responses to the following question: Think about the money you owe (for example to a bank, MFI, SACCO, a shopkeeper, friends or family or a loan you took over the phone). In the past 3 months have you had to reduce spending on food to repay any money that you owe?"), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#CEE5F2", "#FF9F1C",  "#DB504A", "#DD99BB")
names(palette) <- c("Yes, not at all difficult", "Yes, somewhat difficult", "Yes, very difficult", "Not possible", "Don't know/refused")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1.0001), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### MFHI Component indicator #4

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-mfhi_risk_ef_main
#| echo: false
#| warning: false
#| fig-cap: "MFHI #4: Access to emergency funds"
#| cap-location: margin

fig_notes <- ""

indicators <- c("mfhi_ef_secure")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 80, indicator_branch = 40, group_name = 80, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = "Able to raise emergency funds in 30 days without major difficulty",
  subtitle =  "MFHI Component Indicator #4",
  yax_ti = "Adults (% 18+)",
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", fill = "#41BBD9", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_vjust = 1, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "red")
)

scales <- list(
  fillcolor = NULL, 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

## Investing for the future

### Investing in long-term capital
```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mfhi_inv_capital
#| echo: false
#| warning: false
#| fig-cap: "Capital investments"
#| cap-location: margin

fig_notes <- ""

indicators <- names(int_data)[str_detect(names(int_data), "mfhi_i_pc|mfhi_i_fc|mfhi_i_hc")]
indicators <- indicators[!str_detect(indicators, "allmiss")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 10, indicator_stem = 50, indicator_branch = 40, group_name = 15, group_cat_val = 8), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = FALSE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_tile_data(prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0))

labels <- list(
  title = "Investments in physical, financial and human capital in past 12 months",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "tile", # One of "bar" or "tile"
  tiles = list(color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_face = "plain", lab_size = 3.5, colortext = TRUE),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

scales <- list(
  fillcolor = list(palette = "identity", direction = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "indicator_stem", yvar = "group_cat_val", fillvar = "fillcolor"
)

facets <- list(
  type = "grid", 
  rows = "indicator_category", 
  cols = "group_name",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


### MFHI Component indicator #5
```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-mfhi_inv_main
#| echo: false
#| warning: false
#| fig-cap: "MFHI #5: Investing in capital"
#| cap-location: margin

fig_notes <- ""

indicators <- c("mfhi_i_p12mos_any")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1) 

labels <- list(
  title = str_wrap("Has purchased- or contributed to- assets that support production, productivity or long-term financial security in past 12 months", TI_WRAP),
  subtitle =  "MFHI Component Indicator #5",
  yax_ti = "Adults (% 18+)",
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", fill = "#41BBD9", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "red")
)

scales <- list(
  fillcolor = NULL, 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

## Multi-dimensional financial health index


### MFHI component indicators 

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-mfhi_comp_indicators
#| echo: false
#| warning: false
#| fig-cap: "MFHI component indicators"
#| cap-location: margin

indicators <- c("mfhi_f_secure", "mfhi_nf_secure", "mfhi_d_secure", "mfhi_ef_secure", "mfhi_i_p12mos_any")

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL) 

factor_params <- list(
  wrap_sizes = list(indicator_category = 15, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 8), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_tile_data(prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.1))

labels <- list(
  title = str_wrap("MFHI Component indicators", TI_WRAP),
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, ""), CAP_WRAP)
)

figparams <- list(
  geom_type = "tile", # One of "bar" or "tile"
  tiles = list(color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_face = "plain", lab_size = 3.5, colortext = TRUE),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

scales <- list(
  fillcolor = list(palette = "identity", direction = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "indicator_stem", yvar = "group_cat_val", fillvar = "fillcolor"
)

facets <- list(
  type = "grid", 
  rows = "indicator_category", 
  cols = "group_name",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


### MFHI score

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-mfhi_score_hist
#| echo: false
#| warning: false
#| fig-cap: "MFHI score distribution"
#| cap-location: margin

# Histograms

indicators <- c("mfhi_score_overall", "mfhi_score_overall_c")

ggplot(data = int_data) + 
  geom_histogram(aes(x = mfhi_score_overall_c), color = "white", fill = "red", binwidth = 0.05) + 
  geom_histogram(aes(x = mfhi_score_overall), color = "white", fill = "blue", binwidth = 0.05, alpha = 0.3) + 
  theme_custom()
  
```


```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mfhi_score_mean
#| echo: false
#| warning: false
#| fig-cap: "MFHI mean score"
#| cap-location: margin

fig_notes <- ""
  
indicators <- names(int_data)[str_detect(names(int_data), "mfhi_score_md2d|mfhi_score_risk|mfhi_score_inv")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 60, indicator_stem = 25, indicator_branch = 40, group_name = 25, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = FALSE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_type = "number", valuelabel_round = 2) %>% 
  group_by(indicator_category, group_cat_val) %>%
  mutate(
      total = sum(mean), 
      barlabel = ifelse(indicator_stem == "Investing in capital", numclean(total, 2), NA),
      barlabelpos = ifelse(indicator_stem == "Investing in capital", total, NA), 
    ) 

labels <- list(
  title = "Multi-dimensional financial health index scores",
  subtitle =  "Mean score",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = TRUE, labeltotal_ndgy = TRUE, labeltotal_extendmax = TRUE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#DB504A",  "#A2C3A4")
names(palette) <- c("Managing day to day", "Coping with risk", "Investing in capital")

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE), 20)

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "number", expand = c(0,0), droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_stem"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_category",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


### MFHI Score categories

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mfhi_score_cats
#| echo: false
#| warning: false
#| fig-cap: "MFHI score categories"
#| cap-location: margin

fig_notes <- ""

indicators <- names(int_data)[str_detect(names(int_data), "mfhi_score_hi|mfhi_score_med|mfhi_score_low")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 60, indicator_stem = 25, indicator_branch = 40, group_name = 25, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = TRUE, indicator_branch = FALSE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.05) 

labels <- list(
  title = "Multi-dimensional financial health index score categories",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#FF9F1C",  "#DB504A")
names(palette) <- c("High (0.6-1)", "Medium (0.3-0.6)", "Low (0-0.3)")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1.0001), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_category",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

## Perceptions of financial health

### Worry, confidence and assessments of change in financial status
```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-pfh
#| echo: false
#| warning: false
#| fig-cap: "Perceptions of financial health"
#| cap-location: margin

indicators <- names(int_data)[str_detect(names(int_data), "pfh")]
indicators <- indicators[!str_detect(indicators, "score")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = int_data, weights = "sample_weights", psu = "sample_psu", keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_category = 40, indicator_stem = 30, indicator_branch = 40, group_name = 15, group_cat_val = 80), 
  reverse_order = list(indicator_category = FALSE, indicator_stem = FALSE, indicator_branch = TRUE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_category = NULL, indicator_stem = NULL, indicator_branch = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = TRUE, valuelabel_thresh = 0.01) 

labels <- list(
  title = "Perceptions of financial health",
  subtitle =  "Adults (% 18+)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = paste(SOURCE, "Notes:")
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3.25),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#FF9F1C",  "#DB504A", "#41BBD9", "#FF9F1C",  "#DB504A", "#41BBD9", "#FF9F1C",  "#DB504A", "grey90", "#DD99BB")
names(palette) <- c("Not worried at all", "Somewhat worried", "Very worried", "Very confident", "Somewhat confident", "Not confident at all", "Improved", "Remained the same", "Worsened", "Not applicable (No debt)", "Don't know/refused")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1.003), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 3, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_branch"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_stem",
  nrows = 1, 
  ncols = 1,
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

### Correlation between financial health perceptions and financial health outcomes 

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mfhi_pfh_corr
#| echo: false
#| warning: false
#| fig-cap: "Correlation between financial health outcomes and pereptions"
#| cap-location: margin




```
